Computational tools for representation theory of affine Lie algebras

### 2009-07-13 AffineLieAlgebras/ACMS2009/notes.tex
Section on modular invariants is finished

It can be shown that solutions of equation (\ref{eq:111}) exist only for level 1 $k=1$. 
\section{Affine Lie algebras representations}
\label{sec:affine-lie-algebras}

>>>>

It can be shown that solutions of equation (\ref{eq:111}) exist only for level 1 $k=1$.

There exist only finite number of such embeddings.

{\bf Examples}
\begin{itemize}
\item $su(2)\subset su(3),\; x_e=4$
\item $\hat{su}(2)_{10}\subset\hat{sp}(4)_1$
\item $\hat{su}(2)_{28}\subset(\hat{G_2})_1$
\item $\hat{su}(2)_{16}\oplus\hat{su}(3)\subset (\hat{E_8})_1$
\end{itemize}

Branching $\hat{\lambda}\to \bigoplus_{\hat{\mu}}b_{\hat{\lambda}\hat{\mu}}\hat{\mu}$
\begin{equation}
  \label{eq:112}
  h_{\hat{\lambda}}+n=h_{\hat{\mu}},\quad \frac{(\lambda,\lambda+2\rho)}{2(1+g)}+n=\frac{(\mu,\mu+2\rho)}{2(x_e+p)}
\end{equation}
The simple way is to calculate the dimensions of all the representations of simple finite-dimensional Lie algebras $\mathfrak{g},\mathfrak{p}$ and find all the triples $(\lambda,\mu,n)$, satisfying (\ref{eq:112}). Then investigate the representation $L_{\hat{\lambda}}$ of level $n$ as the sum of irreducible representations of $\mathfrak{g}$ and write out all the branching rules of these representations in representations of subalgebra $\mathfrak{p}$. The number of times the representation with highest weight $\mu$ appears in this listing is the required branching coefficient $b_{\hat{\lambda},\hat{\mu}}$.

  Then non-diagonal modular invariants are obtained by substitution of character relations. For example, having calculated branching coefficients for $\hat{su}(2)_{28}\subset (\hat{G_2})_1$
  \begin{equation}
    \label{eq:113}
    \begin{aligned}
      & [1,0,0]\to [28,0]\oplus [18,10]\oplus [10,18]\oplus [0,28]\\
      & [0,0,1]\to [22,6]\oplus [16,12]\oplus [12,16]\oplus [6,22]\\
    \end{aligned}
  \end{equation}
we get following modular-invariant partition function
\begin{equation}
  \label{eq:114}
  Z=\left|\chi_{[28,0]}+\chi_{[18,10]}+\chi_{[10,18]}+\chi_{[0,28]}\right|^2+\left|\chi_{[22,6]}+\chi_{[16,12]}+\chi_{[12,16]}+\chi_{[6,22]}\right|^2
\end{equation}

\section{Affine Lie algebras representations}
\label{sec:affine-lie-algebras}
